The pollination trade-off

### 2018-02-27 publication/supp_info.Rmd
Use a data frame of random effects instead of hard coding it

```{r table-aic-random-models, results= 'asis'}
loadd(glanced_random)

summ <- glanced_random %>%
  filter(var_trans == "log") %>%
  group_by(pollen_category, scale, var_trans, model) %>%
  mutate(delta_AIC = AIC - min(AIC)) %>%
  group_by(pollen_category, scale, var_trans, random_effect) %>%
  summarise(AIC_50 = median(delta_AIC), 
            AIC_05 = quantile(delta_AIC, 0.05),
            AIC_95 = quantile(delta_AIC, 0.95)) %>% 
  mutate_if(is.numeric, round, digits = 1) %>% 
  mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "]")) %>%
  group_by() %>%
  humanize() %>%
  arrange(pollen_category, scale, random_effect) %>%
  rename(`pollen category` = pollen_category, 
         `random structure` = random_effect)

contingency_table <- summ %>%
  # select(-var_trans) %>%
  ftable(row.vars = 4, col.vars = c(1, 2))

>>>>

```{r table-aic-random-models, results= 'asis'}
loadd(glanced_random, random_effects)

summ <- glanced_random %>%
  filter(var_trans == "log") %>%
  group_by(pollen_category, scale, var_trans, model) %>%
  mutate(delta_AIC = AIC - min(AIC)) %>%
  group_by(pollen_category, scale, var_trans, random_effect) %>%
  summarise(AIC_50 = median(delta_AIC), 
            AIC_05 = quantile(delta_AIC, 0.05),
            AIC_95 = quantile(delta_AIC, 0.95)) %>% 
  mutate_if(is.numeric, round, digits = 1) %>% 
  mutate(delta_AIC = paste0(AIC_50, " [", AIC_05, ", ", AIC_95, "]")) %>%
  group_by() %>%
  humanize(random_effects = random_effects) %>%
  arrange(pollen_category, scale, random_name) %>%
  rename(`pollen category` = pollen_category, 
         `random structure` = random_name)

contingency_table <- summ %>%
  # select(-var_trans) %>%
  ftable(row.vars = 10, col.vars = c(1, 2))
